\large \textbf{Burrows-Wheeler transform for terabases}

### 2015-10-21 paper/paper.tex
Sketched some details.

ReadServer; multiple BWTs

@@

@@

buffering: run buffer, thread buffer (RLE, differential encoding, dynamic paged array), merge buffers, to disk

interleaving: multiway merge from disk in one thread, interleave BWTs in another, dynamic paged array

@@

implementation, environment

data: ReadServer BWTs, NA12878 trio

@@

sequence ordering: RLO/RCLO for compression, RLCO for mapping between reverse complements, mapping position for encoding pairing information

>>>>

ReadServer; multiple BWTs due to construction issues; less BWTs would mean less memory, less querying

@@

sort is interleaved with search and merge

@@

buffering: run buffer, thread buffer (RLE, differential encoding), merge buffers, to disk

interleaving: multiway merge from disk in one thread, interleave BWTs in another

\Section{Implementation}

C++, compiler, github

details of run-length encoding of BWT, RA

number of threads

use 8~MB blocks instead of virtual memory pages

@@

environment

data: ReadServer BWTs, NA12878 trio \cite{1000GP2015}
error correction using bfc \cite{Li2015}

@@

sequence ordering: original orderin may be important, RLO/RCLO for compression, RLCO for mapping between reverse complements, mapping position for encoding pairing information
